Chemical Tagging Using Minimum Message Length. I.\\ Gaussian Mixture Modelling

### 2017-04-19 articles/chemical-tagging/ms.tex
frameworking

>>>>

\section{Experiments}
\label{sec:experiments}

Here we describe simple chemical tagging experiments that are so optimistic
that they could be considered laughable, but ones which will still fail for
even the most simplistic chemical tagging approaches.

Each experiment will edge closer to a representative example of chemical
tagging.

\subsection{Experiment 0: Position and Velocity information}

\subsection{Experiment 1: Using clusters, full complement of chemical abundances}

\subsection{Experiment 2: Using all clusters, full complement of chemical abundances, random fractions of field stars}

\subsection{Experiment 3: Using clusters, limited set of chemical abundances}

\subsection{Experiment 4: Fake data to replicate clusters, but use latent factor}

\subsection{Experiment 5: Fake data to replicate clusters, but use multiple latent factors}

\section{Discussion}
\label{sec:discussion}
